Of judges, aliens and total preorders

### 2021-02-01 paper/1901_3230880_philip_heltweg.tex
feat: beamer setup
fix: added advisor feedback

\documentclass[english, 12pt]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage[onehalfspacing]{setspace}
\usepackage{float}

@@

@@

In belief revision, belief change is modelled using an operator that produces an updated set of beliefs from the state of an agent and new evidence. Research in this area discusses appropriate formalisations of agent state and constrains on individual operators or families of operators. Depending on if the suggested operator handles only one new evidence or multiple new evidences, the approaches are called one-step or iterated belief revision.

@@

\subsection{Propositional Logic} % Aussagenlogik
The following notation will be used, as proposed by \cite{Booth2011}: A propositional language $L$ generated from finitely many propositional variables. Lower case greek letters represent formulae in $L$ and $\top$, $\bot$ representing tautology and contradiction respectively. $\vdash$ denotes classical logical consequence, $\equiv$ classical logical equivalence. $Cn$ is used to denote the deductive closure of a formula or set of formulae in $L$.

$W$ is the set of propositional worlds (also called propositional interpretations in classical logic \cite{Kai2020}). Given a formula $\alpha \in L$, the set of worlds that satisfy $\alpha$ is denoted by $[\alpha]$.

@@

Belief sets can be extracted from epistemic states. The belief set extracted from an epistemic state $\mathbb{E}$ is denoted as $B(\mathbb{E})$. Darwiche and Pearl show that their version of revision of epistemic states can be modelled with a tpo $\leq_{\mathbb{E}}$, associated with $\mathbb{E}$. Extraction of $B(\mathbb{E})$ is achieved by considering the set of lowest ranked worlds (i.e. the most plausible interpretations) under $\leq_{\mathbb{E}}$. The set of propositional sentences that holds in all those worlds is defined to be the belief set of the agent. For notation let $min(\alpha, \leq_{\mathbb{E}})$ denote the set of minimal models for the propositional formula $\alpha$ under $\leq_{\mathbb{E}}$. Then $[B(\mathbb{E})] = min(\top, \leq_{\mathbb{E}})$ is the set of worlds that are models of the belief set $B(\mathbb{E})$ associated with $\mathbb{E}$. The belief set of the agent with this notation is $Th([B(\mathbb{E})])$.

@@

    $min(\top, \leq_{\mathbb{E}})$ is the set of worlds on the lowest rank, $\{010, 100\}$. A possible belief set is $B(\mathbb{E}) = \{p \vee q, \neg p \vee \neg q, \neg r\}$ as $[B(\mathbb{E})] = \{010, 100\} = min(\top, \leq_{\mathbb{E}})$. Intuitively this makes sense, with the initial assumption that John or Mary are the suspects ($p \vee q$), have acted alone ($\neg p \vee \neg q$) and the victim is not an alien ($\neg r$).
\end{example}

@@

\subsection{Belief revision postulates}
\label{chapter:dp-agm-postulates}
The postulates first introduced by \cite{Alchourron1985} and reformulated for iterated belief revision on epistemic states by \cite{Darwiche1997} which are further used in this text are presented here. $\mathbb{E}$ denotes an epistemic state, $B(\mathbb{E})$ it's associated belief set, $B(\mathbb{E}) + \alpha$ the expansion of $B(\mathbb{E})$ by $\alpha$. $\ast$ being a belief change operator on epistemic states.

\begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\mathbb{E}\!*\!\arabic*$)]
    \item\label{E1} $\qquad B(\mathbb{E}\ast\alpha) = Cn(B(\mathbb{E}\ast\alpha))$
    \item\label{E2} $\qquad \alpha \in B(\mathbb{E}\ast\alpha)$
    \item\label{E3} $\qquad B(\mathbb{E}\ast\alpha)  \subseteq B(\mathbb{E})+\alpha$
    \item\label{E4} $\qquad \textrm{If } \alpha \notin B(\mathbb{E}) \textrm{ then } B(\mathbb{E}) + \alpha \subseteq B(\mathbb{E} \ast \alpha)$
    \item\label{E5} $\qquad \textrm{If } \mathbb{E} = \mathbb{F} \textrm{ and } \alpha \equiv \beta \textrm{ then } B(\mathbb{E} \ast \alpha) = B(\mathbb{F} \ast \beta)$
    \item\label{E6} $\qquad \bot \in B(\mathbb{E} \ast \alpha) \textrm{ iff } \vdash \neg \alpha$
    \item\label{E7} $\qquad B(\mathbb{E} \ast (\alpha \wedge \beta)) \subseteq B(\mathbb{E} \ast \alpha) + \beta$
    \item\label{E8} $\qquad \textrm{If } \neg \beta \notin B(\mathbb{E} \ast \alpha) \textrm{ then } B(\mathbb{E} \ast \alpha) + \beta \subseteq B(\mathbb{E} \ast (\alpha \wedge \beta))$
\end{enumerate}

@@

\begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = (CR$\arabic*$)]
    \item\label{CR1} $\qquad \textrm{If } v\in [\alpha], w \in [\alpha] \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ iff } v \leq_{\mathbb{E\ast\alpha}} w$
    \item\label{CR2} $\qquad \textrm{If } v\in [\neg \alpha], w \in [\neg \alpha] \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ iff } v \leq_{\mathbb{E\ast\alpha}} w$
    \item\label{CR3} $\qquad \textrm{If } v\in [ \alpha], w \in [\neg \alpha] \textrm{ then } v <_{\mathbb{E}} w \textrm{ only if } v <_{\mathbb{E\ast\alpha}} w$
    \item\label{CR4} $\qquad \textrm{If } v\in [ \alpha], w \in [\neg \alpha] \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ only if } v \leq_{\mathbb{E\ast\alpha}} w$
\end{enumerate}

\ref{CR1} and \ref{CR2} mean that the relative ordering of worlds following a revision by $\alpha$ stays the same if the worlds are either both $\alpha$ or $\neg\alpha$ worlds. \ref{CR3} and \ref{CR4} require that $\alpha$-worlds that are strictly/weakly more plausible than $\neg\alpha$-worlds are still strictly/weakly more plausible than them after a $\alpha$-revision.

% TODO: QUESTION: do we need C1-C4 here? 
%\begin{equation*}
%\begin{aligned}
%    (C1) \qquad & \textrm{If } \beta \vdash \alpha \textrm{ then } B(\mathbb{E}\ast\alpha\ast\beta)=B(\mathbb{E}\ast\beta) \\
%    (C2) \qquad & \textrm{If } \beta \vdash \neg  \alpha \textrm{ then } B(\mathbb{E}\ast\alpha\ast\beta)=B(\mathbb{E}\ast\beta) \\
%    (C3) \qquad & \textrm{If } \alpha \in B(\mathbb{E}\ast\beta) \textrm{ then } \alpha \in B(\mathbb{E}\ast\alpha\ast\beta) \\
%    (C4) \qquad & \textrm{If } \neg \alpha \notin B(\mathbb{E}\ast\beta) \textrm{ then } \neg \alpha \notin B(\mathbb{E}\ast\alpha\ast\beta) \\
%\end{aligned}
%\end{equation*}

@@

Booth and Meyer's \cite{Booth2011} approach is to add an additional structure with metadata for every world $w \in W$. This new structure is denoted as $W^{\pm} = \{x^{\epsilon} \mid x \in W \textrm{ and } \epsilon \in \{+, -\}\}$. In this notation a world $w \in W$ is represented twice: When new evidence $\alpha$ arrives that makes $w$ more plausible (because $w \in [\alpha]$), the agent can assume it's positive representation as $w^{+} \in W^{\pm}$. In contrast, if the new evidence makes $w$ less plausible ($w \notin [\alpha]$), then the negative representation $w^{-} \in W^{\pm}$ is the agent's view of $w$. Booth and Meyer call the pair $(w^{+}, w^{-})$ the positive/negative representation of the world $w$. They are an abstract interval, representing metadata about plausibility assumptions about $w$.

@@

\begin{example}
    \label{example:example-stick}
    Recall that tpos can be equivalently thought of as a linearly ordered set of ranks (Example \ref{example:example-introduction}). Therefore a tpo over $W$ can be visualised by ordering every $w \in W$ in a table of ranks (table \ref{tab:visualising-a-tpo-example}). To visualise the interval ordering introduced by $\preceq$, Booth and Meyer use a "stick" with the endpoints defined as $w^{+}$/$w^{-}$ respectively. This method was first introduced in \cite{Booth2007} and is shown in Figure \ref{fig:example-visualisation-scatterplot}.

@@

                    1 4 empty $x_{1}^{+}$
                    3 4 empty $x_{1}^{-}$
                    };
            \end{axis}
        \end{tikzpicture}
        \caption{Representation of $\preceq$ over $W^{\pm}$ using sticks}
        \label{fig:example-visualisation-scatterplot}
    \end{figure}

   The worlds on lower ranks (more on the left) are preferred and assumed to be more plausible. Here for example $x_{1}^{+} \prec x_{3}^{+}$ and $x_{1}^{-} \sim x_{4}^{+}$ Note that, even though all sticks have the same length in this example, that is not required.
\end{example}

@@

\begin{definition}[$\leq$-faithful tpo over $W^{\pm}$ taken directly from \cite{Booth2011}]
\label{definition:faithful-tpo}Let $\preceq \in W^{\pm} \times W^{\pm}$. If $\preceq$ satisfies \ref{PREQ1}-\ref{PREQ4}, we say $\preceq$ is a $\leq$-faithful tpo (over $W^{\pm}$).
\end{definition}

@@

\begin{example}
    \label{example:example-faithful-tpo}
    Is the following tpo $\preceq$ over $W^{\pm}$ a $\leq$-faithful tpo?

@@

    Even though \ref{PREQ1} and \ref{PREQ4} are satisfied, $\preceq$ is not a $\leq$-faithful tpo: From \ref{PREQ2} and $x_{1}^{+} \prec x_{2}^{+}$ follows $x_{1} < x_{2}$. That means \ref{PREQ3} can not hold as $x_{2}^{-} \prec x_{1}^{-}$ which would require $x_{2} < x_{3}$ to be true.

    As demonstrated here, even though the "sticks" do not need to be the same size for all worlds (they just must exist due to \ref{PREQ4}), they need to be the same size for worlds that share a rank for their corresponding representations. They can not overlap other sticks completely to continue to satisfy \ref{PREQ2} and \ref{PREQ3}.
\end{example}

\begin{example}
    \label{example:example-tpo-initial}
    Continuing the courtroom demonstration introduced in \ref{example:example-introduction} of a judge deciding on a verdict on the suspects John and Mary. Figure \ref{fig:example-tpo-initial} shows a possible version of a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ from which the tpo $\leq$ from table \ref{tab:visualising-a-tpo-example} can be reconstructed.

@@

    Notice the "gap" between the $[r]$-worlds that include the victim being an alien. Even in their positive representations they are not as plausible as negative representations of $[\neg r]$-worlds. That fact will be discussed more in section \ref{section:non-prioritised-revision} and example \ref{example:example-non-prio-revision}.
\end{example}

\section{Booth and Meyer tpo-revision operators}
\label{section:booth-and-meyer-tpo-revision-operators}
Booth and Meyer \cite{Booth2011} discussed tpo revision operators, functions $\ast$ that return a new tpo $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$. To do so they define how to use the additional information from a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ to create a revision operator $\ast_{\preceq}$ (from now on referred to as BM tpo-revision operators).

\begin{definition}[Revision operator $\ast_{\preceq}$ for $\leq$ generated by $\preceq$ from \cite{Booth2011}]
    \label{definition:revision-operator}
    For each $\leq$-faithful tpo $\preceq$ over $W^{\pm}$, refer to $\ast_{\preceq}$ as the revision operator for $\leq$ generated by $\preceq$ defined by:

    Set for any $\alpha \in L$ and $x \in W$:
    \begin{equation*}
        r_{\alpha}(x) = \left\{
                    \begin{array}{ll}
                      x^{+} \textrm{ if } x \in [\alpha]\\
                      x^{-} \textrm{ if } x \in [\neg\alpha]
                    \end{array}
                  \right.
    \end{equation*}

@@

Intuitively, new evidence $\alpha$ makes worlds that satisfy $\alpha$ more plausible and worlds that do not satisfy $\alpha$ less plausible. Therefore the agent associates worlds $x \in [\alpha]$ with their positive representation $x^{+}$ and worlds $x \in [\neg\alpha]$ with their negative representation $x^{-}$.

\begin{example}
    \label{example:example-updated-tpo}
    Reconsider the $\leq$-faithful tpo $\preceq$ from example \ref{example:example-stick}. When a new piece of evidence $\alpha$ has to be considered, each world gets mapped to one end of the interval assigned to it, depending on if it is an $\alpha$-world or not. In figure \ref{fig:example-updated-tpo} that mapping is indicated by the filled out dot. For this example $x_{1}, x_{2}$ and $x_{3}$ are $[\neg\alpha]$-worlds while $x_{4}$ is an $[\alpha]$-world.

@@

\begin{example}
    \label{example:example-tpo-revised}
    A more complex example is the revision of $\leq$ to $\leq_{\alpha}^{\ast}$ (for the courtroom example \ref{example:example-introduction}) using the $\leq$-faithful tpo $\preceq$, introduced in example \ref{example:example-tpo-initial} and shown in figure \ref{fig:example-tpo-revised}. In this case the new evidence received points to John being the murderer so $\alpha = p$.

@@

    \begin{equation*}
        010 \in [\neg\alpha] \textrm{ : } r_{\alpha}(010) = 010^{-}
    \end{equation*}
    \begin{equation*}
        110 \in [\alpha] \textrm{ : } r_{\alpha}(110) = 110^{+}
    \end{equation*}

@@

    Repeating for every world in $W$, the new tpo $\leq_{\alpha}^{\ast}$ is: $100 <_{\alpha}^{\ast} 110 <_{\alpha}^{\ast} 010 <_{\alpha}^{\ast} 000 <_{\alpha}^{\ast} 101 <_{\alpha}^{\ast} 111 <_{\alpha}^{\ast} 011 <_{\alpha}^{\ast} 001$. Unsurprisingly, the belief set associated with the new epistemic state is $[B(\mathbb{E})] = min(\top, \leq_{\mathbb{E}}) = \{100\}$: "John is the murderer and the victim is not an alien".

@@

A demonstration is already provided with example \ref{example:example-updated-tpo} and figure \ref{fig:example-updated-tpo}. The most plausible worlds in the new epistemic state $\mathbb{E}$, $min(\top, \leq_{\alpha}^{\ast})$, include the $[\neg\alpha]$-worlds $x_{1}$ and $x_{2}$. Therefore $Th(min(\top, \leq_{\alpha}^{\ast}))$ does not include the new evidence $\alpha$.

@@

    Since the agent considered the victim being an alien very unlikely, even the positive representations of worlds in $[\alpha]$ are on higher ranks (so considered less plausible) than negative representations of worlds in $[\neg\alpha]$.
    The belief set $B(\mathbb{E})$ of the agent is unchanged under $\leq_{\alpha}^{\ast}$, since $\{010, 100\}$ are still the most plausible worlds, and does not include $r$ "the victim is an alien".
\end{example}

@@

\begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\ast\arabic*$)]
    \item\label{AST1} $\qquad \leq_{\alpha}^{\ast} \textrm{ is a tpo over } W$
    \item\label{AST2} $\qquad\alpha \equiv \gamma \textrm{ implies } \leq_{\alpha}^{\ast}=\leq_{\gamma}^{\ast}$
    \item\label{AST3} $\qquad \textrm{If } x, y \in [\alpha] \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
    \item\label{AST4} $\qquad \textrm{If } x, y \in [\neg\alpha] \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
    \item\label{AST5} $\qquad \textrm{If } x \in [\alpha], y \in [\neg\alpha] \textrm{ and } x \leq y \textrm{ then } x <_{\alpha}^{\ast} y$
    \item\label{AST6} $\qquad \textrm{If } x \in [\alpha], y \in [\neg\alpha] \textrm{ and } y \leq_{\alpha}^{\ast} x \textrm{ then } y \leq_{\gamma}^{\ast} x$
    \item\label{AST7} $\qquad \textrm{If } x \in [\alpha], y \in [\neg\alpha] \textrm{ and } y <_{\alpha}^{\ast} x \textrm{ then } y <_{\gamma}^{\ast} x$
\end{enumerate}

@@

\ref{AST1} and \ref{AST2} are considered basic properties: A revision of a tpo $\leq$ over $W$ must generate another tpo over $W$ . In addition the operator must return an equal revised tpo for semantically equivalent sentences, the so called syntax-irrelevance property.

>>>>

\documentclass[english, 12pt]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage[onehalfspacing]{setspace}
\usepackage{float}
\usepackage{stmaryrd}

@@

\newcommand{\modelsOf}[1]{\llbracket #1 \rrbracket}

@@

In belief revision, belief change is modelled using an operator that produces an updated set of beliefs from the state of an agent and new evidence. Research in this area discusses appropriate formalisations of agent state and constrains on individual operators or families of operators. Depending on if the suggested operator handles only one new evidence or consecutive evidence, the approaches are called one-step or iterated belief revision.

@@

\subsection{Propositional Logic} % Aussagenlogik
The following notation will be used, as proposed by \cite{Booth2011}: A propositional language $L$ generated from finitely many propositional variables. Lower case greek letters represent formulae in $L$ and $\top$, $\bot$ representing tautology and contradiction respectively. $\models$ denotes classical logical consequence, $\equiv$ classical logical equivalence. $Cn$ is used to denote the deductive closure of a formula or set of formulae in $L$.

$W$ is the set of propositional worlds (also called propositional interpretations in classical logic \cite{Kai2020}). Given a formula $\alpha \in L$, the set of worlds that satisfy $\alpha$ is denoted by $\modelsOf{\alpha}$.

@@

Belief sets can be extracted from epistemic states. The belief set extracted from an epistemic state $\mathbb{E}$ is denoted as $B(\mathbb{E})$. Darwiche and Pearl show that their version of revision of epistemic states can be modelled with a tpo $\leq_{\mathbb{E}}$, associated with $\mathbb{E}$. Extraction of $B(\mathbb{E})$ is achieved by considering the set of lowest ranked worlds (i.e. the most plausible interpretations) under $\leq_{\mathbb{E}}$. The set of propositional sentences that holds in all those worlds is defined to be the belief set of the agent. For notation let $min(\alpha, \leq_{\mathbb{E}})$ denote the set of minimal models for the propositional formula $\alpha$ under $\leq_{\mathbb{E}}$. Then $\modelsOf{B(\mathbb{E})} = min(\top, \leq_{\mathbb{E}})$ is the set of worlds that are models of the belief set $B(\mathbb{E})$ associated with $\mathbb{E}$. The belief set of the agent with this notation is $Th(\modelsOf{B(\mathbb{E})})$.

@@

    $min(\top, \leq_{\mathbb{E}})$ is the set of worlds on the lowest rank, $\{010, 100\}$. A possible belief set is $B(\mathbb{E}) = \{p \vee q, \neg p \vee \neg q, \neg r\}$ as $\modelsOf{B(\mathbb{E})} = \{010, 100\} = min(\top, \leq_{\mathbb{E}})$. Intuitively this makes sense, with the initial assumption that John or Mary are the suspects ($p \vee q$), have acted alone ($\neg p \vee \neg q$) and the victim is not an alien ($\neg r$).
\end{example}

@@

\subsection{Belief revision postulates}
\label{chapter:dp-agm-postulates}
A well established set of Postulates for revision are the AGM postulates \cite{Alchourron1985}. In this text, a reformulation for epistemic states by Darwiche and Pearl \cite{Darwiche1997} is used, presented in the following. $\mathbb{E}$ denotes an epistemic state, $B(\mathbb{E})$ it's associated belief set, $B(\mathbb{E}) + \alpha$ the expansion of $B(\mathbb{E})$ by $\alpha$. $\ast$ being a belief change operator on epistemic states.

\begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\mathbb{E}\!*\!\arabic*$)]
    \item\label{E1} $\qquad B(\mathbb{E}\ast\alpha) = Cn(B(\mathbb{E}\ast\alpha))$
    \item\label{E2} $\qquad \alpha \in B(\mathbb{E}\ast\alpha)$
    \item\label{E3} $\qquad B(\mathbb{E}\ast\alpha)  \subseteq B(\mathbb{E})+\alpha$
    \item\label{E4} $\qquad \textrm{If } \alpha \notin B(\mathbb{E}) \textrm{ then } B(\mathbb{E}) + \alpha \subseteq B(\mathbb{E} \ast \alpha)$
    \item\label{E5} $\qquad \textrm{If } \mathbb{E} = \mathbb{F} \textrm{ and } \alpha \equiv \beta \textrm{ then } B(\mathbb{E} \ast \alpha) = B(\mathbb{F} \ast \beta)$
    \item\label{E6} $\qquad \bot \in B(\mathbb{E} \ast \alpha) \textrm{ iff } \models \neg \alpha$
    \item\label{E7} $\qquad B(\mathbb{E} \ast (\alpha \wedge \beta)) \subseteq B(\mathbb{E} \ast \alpha) + \beta$
    \item\label{E8} $\qquad \textrm{If } \neg \beta \notin B(\mathbb{E} \ast \alpha) \textrm{ then } B(\mathbb{E} \ast \alpha) + \beta \subseteq B(\mathbb{E} \ast (\alpha \wedge \beta))$
\end{enumerate}

@@

\begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = (CR$\arabic*$)]
    \item\label{CR1} $\qquad \textrm{If } v\in \modelsOf{\alpha}, w \in \modelsOf{\alpha} \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ iff } v \leq_{\mathbb{E\ast\alpha}} w$
    \item\label{CR2} $\qquad \textrm{If } v\in \modelsOf{\neg\alpha}, w \in \modelsOf{\neg\alpha} \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ iff } v \leq_{\mathbb{E\ast\alpha}} w$
    \item\label{CR3} $\qquad \textrm{If } v\in \modelsOf{\alpha}, w \in \modelsOf{\neg\alpha} \textrm{ then } v <_{\mathbb{E}} w \textrm{ only if } v <_{\mathbb{E\ast\alpha}} w$
    \item\label{CR4} $\qquad \textrm{If } v\in \modelsOf{\alpha}, w \in \modelsOf{\neg\alpha} \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ only if } v \leq_{\mathbb{E\ast\alpha}} w$
\end{enumerate}

\ref{CR1} and \ref{CR2} mean that the relative ordering of worlds following a revision by $\alpha$ stays the same if the worlds are either both $\alpha$- or $\neg\alpha$- worlds. \ref{CR3} and \ref{CR4} require that $\alpha$-worlds that are strictly/weakly more plausible than $\neg\alpha$-worlds are still strictly/weakly more plausible than them after an $\alpha$-revision.

@@

Booth and Meyer's \cite{Booth2011} approach is to add an additional structure with metadata for every world $w \in W$. This new structure is denoted as $W^{\pm} = \{x^{\epsilon} \mid x \in W \textrm{ and } \epsilon \in \{+, -\}\}$. In this notation a world $w \in W$ is represented twice: When new evidence $\alpha$ arrives that makes $w$ more plausible (because $w \in \modelsOf{\alpha}$), the agent can assume it's positive representation as $w^{+} \in W^{\pm}$. In contrast, if the new evidence makes $w$ less plausible ($w \notin \modelsOf{\alpha}$), then the negative representation $w^{-} \in W^{\pm}$ is the agent's view of $w$. Booth and Meyer call the pair $(w^{+}, w^{-})$ the positive/negative representation of the world $w$. They are an abstract interval, representing metadata about plausibility assumptions about $w$.

@@

\begin{example}
    \label{example:example-intervals}
    Recall that tpos can be equivalently thought of as a linearly ordered set of ranks (Example \ref{example:example-introduction}). Therefore a tpo over $W$ can be visualised by displaying every $w \in W$ in a table that has one column for every rank (like in Table \ref{tab:visualising-a-tpo-example}). To visualise the interval ordering introduced by $\preceq$, Booth and Meyer use an interval with the endpoints defined as $w^{+}$/$w^{-}$ respectively. This type of visualisation was first introduced in a previous paper by Booth and Meyer themselves \cite{Booth2007} and is shown in Figure \ref{fig:example-visualisation-scatterplot}.

@@

                    1 4 empty $x_{1}^{+}$
                    3 4 empty $x_{1}^{-}$
                    };
            \end{axis}
        \end{tikzpicture}
        \caption{Representation of $\preceq$ over $W^{\pm}$ using intervals}
        \label{fig:example-visualisation-scatterplot}
    \end{figure}

   The worlds on lower ranks (more on the left) are preferred and assumed to be more plausible. Here for example $x_{1}^{+} \prec x_{3}^{+}$ and $x_{1}^{-} \sim x_{4}^{+}$ Note that, even though all intervals have the same length in this example, that is not required.
\end{example}

@@

\begin{definition}[$\leq$-faithful tpo over $W^{\pm}$ \cite{Booth2011}]
\label{definition:faithful-tpo}Let $\preceq \subseteq W^{\pm} \times W^{\pm}$. If $\preceq$ satisfies \ref{PREQ1}-\ref{PREQ4}, we say $\preceq$ is a $\leq$-faithful tpo (over $W^{\pm}$).
\end{definition}

@@

\begin{example}
    \label{example:example-faithful-tpo}
    Consider the following tpo $\preceq$ over $W^{\pm}$.

@@

    $\preceq$ is not a $\leq$-faithful tpo: Even though \ref{PREQ1} and \ref{PREQ4} are satisfied, $\preceq$ is not a $\leq$-faithful tpo: From \ref{PREQ2} and $x_{1}^{+} \prec x_{2}^{+}$ follows $x_{1} < x_{2}$. That means \ref{PREQ3} can not hold as $x_{2}^{-} \prec x_{1}^{-}$ which would require $x_{2} < x_{3}$ to be true.

    As demonstrated here, even though the intervals do not need to be the same size for all worlds (they just must exist due to \ref{PREQ4}), they need to be the same size for worlds that share a rank for their corresponding representations. They can not overlap other intervals completely to continue to satisfy \ref{PREQ2} and \ref{PREQ3}.
\end{example}

\begin{example}
    \label{example:example-tpo-initial}
    Continuing the courtroom demonstration introduced in Example \ref{example:example-introduction} of a judge deciding on a verdict on the suspects John and Mary. Figure \ref{fig:example-tpo-initial} shows a possible version of a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ from which the tpo $\leq$ from table \ref{tab:visualising-a-tpo-example} can be reconstructed.

@@

    Notice the "gap" between the $\modelsOf{r}$-worlds that include the victim being an alien. Even in their positive representations they are not as plausible as negative representations of $\modelsOf{\neg r}$-worlds. That fact will be discussed more in section \ref{section:non-prioritised-revision} and example \ref{example:example-non-prio-revision}.
\end{example}

\section{Booth and Meyer tpo-revision operators}
\label{section:booth-and-meyer-tpo-revision-operators}
Booth and Meyer \cite{Booth2011} discussed tpo revision operators, functions $\ast$ that return a new tpo $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$. They define how to use the additional information from a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ to create a revision operator $\ast_{\preceq}$ (from now on referred to as BM tpo-revision operators).

\begin{definition}[Revision operator $\ast_{\preceq}$ for $\leq$ generated by $\preceq$ \cite{Booth2011}]
    \label{definition:revision-operator}
    For each $\leq$-faithful tpo $\preceq$ over $W^{\pm}$, refer to $\ast_{\preceq}$ as the revision operator for $\leq$ generated by $\preceq$ defined by:

    Set for any $\alpha \in L$ and $x \in W$:
    \begin{equation*}
        r_{\alpha}(x) = \left\{
                    \begin{array}{ll}
                      x^{+} \textrm{ if } x \in \modelsOf{\alpha}\\
                      x^{-} \textrm{ if } x \in \modelsOf{\neg\alpha}
                    \end{array}
                  \right.
    \end{equation*}

@@

Intuitively, new evidence $\alpha$ makes worlds that satisfy $\alpha$ more plausible and worlds that do not satisfy $\alpha$ less plausible. Therefore the agent associates worlds $x \in \modelsOf{\alpha}$ with their positive representation $x^{+}$ and worlds $x \in \modelsOf{\neg\alpha}$ with their negative representation $x^{-}$.

\begin{example}
    \label{example:example-updated-tpo}
    Reconsider the $\leq$-faithful tpo $\preceq$ from example \ref{example:example-intervals}. When a new piece of evidence $\alpha$ has to be considered, each world gets mapped to one end of the interval assigned to it, depending on if it is an $\alpha$-world or not. In figure \ref{fig:example-updated-tpo} that mapping is indicated by the filled out dot. For this example $x_{1}, x_{2}$ and $x_{3}$ are $\modelsOf{\neg\alpha}$-worlds while $x_{4}$ is an $\modelsOf{\alpha}$-world.

@@

\begin{example}
    \label{example:example-tpo-revised}
    A more complex example is the revision of $\leq$ to $\leq_{\alpha}^{\ast}$ (for the courtroom Example \ref{example:example-introduction}) using the $\leq$-faithful tpo $\preceq$, introduced in Example \ref{example:example-tpo-initial} and shown in Figure \ref{fig:example-tpo-revised}. In this case the new evidence received points to John being the murderer so $\alpha = p$.

@@

    \begin{equation*}
        010 \in \modelsOf{\neg\alpha} \textrm{ : } r_{\alpha}(010) = 010^{-}
    \end{equation*}
    \begin{equation*}
        110 \in \modelsOf{\alpha} \textrm{ : } r_{\alpha}(110) = 110^{+}
    \end{equation*}

@@

    Repeating for every world in $W$, the new tpo $\leq_{\alpha}^{\ast}$ is: $100 <_{\alpha}^{\ast} 110 <_{\alpha}^{\ast} 010 <_{\alpha}^{\ast} 000 <_{\alpha}^{\ast} 101 <_{\alpha}^{\ast} 111 <_{\alpha}^{\ast} 011 <_{\alpha}^{\ast} 001$. Unsurprisingly, the belief set associated with the new epistemic state is $\modelsOf{B(\mathbb{E})} = min(\top, \leq_{\mathbb{E}}) = \{100\}$: "John is the murderer and the victim is not an alien".

@@

A demonstration is already provided with Example \ref{example:example-updated-tpo} and Figure \ref{fig:example-updated-tpo}. The most plausible worlds in the new epistemic state $\mathbb{E}$, $min(\top, \leq_{\alpha}^{\ast})$, include the $\modelsOf{\neg\alpha}$-worlds $x_{1}$ and $x_{2}$. Therefore $Th(min(\top, \leq_{\alpha}^{\ast}))$ does not include the new evidence $\alpha$.

@@

    Since the agent considered the victim being an alien very unlikely, even the positive representations of worlds in $\modelsOf{\alpha}$ are on higher ranks (so considered less plausible) than negative representations of worlds in $\modelsOf{\neg\alpha}$.
    The belief set $B(\mathbb{E})$ of the agent is unchanged under $\leq_{\alpha}^{\ast}$, since $\{010, 100\}$ are still the most plausible worlds, and does not include $r$ "the victim is an alien".
\end{example}

@@

\begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\ast\arabic*$)]
    \item\label{AST1} $\qquad \leq_{\alpha}^{\ast} \textrm{ is a tpo over } W$
    \item\label{AST2} $\qquad\alpha \equiv \gamma \textrm{ implies } \leq_{\alpha}^{\ast}=\leq_{\gamma}^{\ast}$
    \item\label{AST3} $\qquad \textrm{If } x, y \in \modelsOf{\alpha} \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
    \item\label{AST4} $\qquad \textrm{If } x, y \in \modelsOf{\neg\alpha} \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
    \item\label{AST5} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } x \leq y \textrm{ then } x <_{\alpha}^{\ast} y$
    \item\label{AST6} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } y \leq_{\alpha}^{\ast} x \textrm{ then } y \leq_{\gamma}^{\ast} x$
    \item\label{AST7} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } y <_{\alpha}^{\ast} x \textrm{ then } y <_{\gamma}^{\ast} x$
\end{enumerate}

@@

\ref{AST1} and \ref{AST2} are considered basic properties: A revision of a tpo $\leq$ over $W$ must generate another tpo over $W$. In addition the operator must return an equal revised tpo for semantically equivalent sentences, the so called syntax-irrelevance property.

The next group of properties, \ref{AST3}-\ref{AST5} are common rules in iterated belief change. Booth and Meyer themselves consider them characteristic for admissible revision operators \cite{Booth2006a}.
If revising a tpo by a sentence $\alpha$, the relative ordering of worlds that are either both $\modelsOf{\alpha}$- or $\modelsOf{\neg\alpha}$-worlds, must stay the same (\ref{AST3}/\ref{AST4}). These properties were already part of the semantic postulates \ref{CR1} and \ref{CR2} by Darwiche and Pearl \cite{Darwiche1997} discussed in section \ref{chapter:dp-agm-postulates}.
In a similar way \ref{AST5} is a stronger requirement than the other two Darwiche and Pearl postulates \ref{CR3} and \ref{CR4}. It means the following: A world $x$ that is considered at least as plausible as a world $y$ before a revision by new information $\alpha$. If $\alpha$ makes $x$ more plausible ($x \in \modelsOf{\alpha}$) and $y$ less plausible ($y \in \modelsOf{\neg\alpha}$) then after revision $x$ should be considered strictly more plausible than $y$. This rule was not only proposed by Booth and Meyer \cite{Booth2006a} but also by Jin und Thielscher in \cite{Jin2007} (as the postulate of independence).

% TODO: WHAT ARE ADMISSIBLE OPERATORS
%info here: \cite{Booth2006a}
% see also http://ceur-ws.org/Vol-2445/paper_2.pdf
% see also: Whiwap: Checking Iterative Belief Changes
